国際会議発表

### 2019-07-26 presentation.Rmd
update

>>>>

### 2019

- Kunisato, Y. & Sawa, K.(2019). Obsessive-compulsive tendency attenuates the recovery from overshadowing in associative learning. The 52nd Annual Meeting of the Society for Mathematical Psychology, July 20, Montreal, Canada.

- Hata, K., Ono, H., Ogawa, Y., Takeshita, W., Kunisato, Y., & Suzuki, S. (2019). Development and validation of the activity restriction scale for cancer patients (Sickness Impact Profile for Cancer Patients: SIP-C). The 9th World Congress of Behavioural and Cognitive Therapies, July 20, Berlin, Germany.
